Supplementary Information

### 2021-02-11 doc/manuscript/MEE_manuscript_SI.Rmd
put all climwin plots in SI =/
#91

all_climwin = "S15-S17"
climwin_sameV_sameW = "S15"
climwin_sameV_diffW = "S16"
climwin_diffV_diffW = "S17"

all_GLS = "S18-S37"
GLS_BCNM = "S18"
GLS_BCNM_year = "S19"
GLS_HKK = "S20"
GLS_HKK_year = "S21"
GLS_SCBI = "S22"
GLS_SCBI_year = "S23"
GLS_LDW = "S24"
GLS_LDW_year = "S25"
GLS_HF = "S36"
GLS_HF_year = "S27"
GLS_ZOF = "S28"
GLS_ZOF_year = "S29"
GLS_NIO = "S30"
GLS_NIO_year = "S31"
GLS_LT = "S32"
GLS_LT_year = "S33"
GLS_CB = "S34"
GLS_CB_year = "S35"
GLS_SC = "S36"
GLS_SC_year = "S37"

SC_1970break = "S38"

RW_interactions_all= "S39"
BAI_interactions_all= "S40"

decadal_analysis_figs_all = "S41-S50"
decadal_plot_BCNM = "S41"
decadal_plot_HKK = "S42"
decadal_plot_SCBI = "S43"
decadal_plot_LDW = "S44"
decadal_plot_HF = "S45"
decadal_plot_ZOF = "S46"
decadal_plot_NIO = "S47"
decadal_plot_LT = "S48"
decadal_plot_CB = "S49"
decadal_plot_SC = "S50"

@@

climwin_sameV_sameW_legend = "Figure S15. (PRE at SCBI)"
climwin_sameV_diffW_legend = "Figure S16. (PET at SCBI)"
climwin_diffV_diffW_legend = "Figure S17. (TMX/TMP at HKK)"

GLS_BCNM_legend = "Figure S18. Best GLS models including climate and DBH for Barro Colorado Nature Monument (Panama)"
GLS_BCNM_year_legend = "Figure S19. Best GLS models including climate, DBH, and year for Barro Colorado Nature Monument (Panama)"
GLS_HKK_legend = "Figure S20. Best GLS models including climate and DBH for Huai Kha Khaeng (Thailand)"
GLS_HKK_year_legend = "Figure S21. Best GLS models including climate, DBH, and year for Huai Kha Khaeng (Thailand)"
GLS_SCBI_legend = "Figure S22. Best GLS models including climate and DBH for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_SCBI_year_legend = "Figure S23. Best GLS models including climate, DBH, and year for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_LDW_legend = "Figure S24. Best GLS models including climate and DBH for Lilley Dickey Woods (Indiana, USA)"
GLS_LDW_year_legend = "Figure S25. Best GLS models including climate, DBH, and year for Lilley Dickey Woods (Indiana, USA)"
GLS_HF_legend = "Figure S26. Best GLS models including climate and DBH for Harvard Forest (Massachusetts, USA)"
GLS_HF_year_legend = "Figure S27. Best GLS models including climate, DBH, and year for Harvard Forest (Massachusetts, USA) "
GLS_ZOF_legend = "Figure S28. Best GLS models including climate and DBH for Zofin Forest (Czech Republic)"
GLS_ZOF_year_legend = "Figure S29. Best GLS models including climate, DBH, and year for Zofin Forest (Czech Republic)"
GLS_NIO_legend = "Figure S30. Best GLS models including climate and DBH for Niobrara (Nebraska, USA)"
GLS_NIO_year_legend = "Figure S31. Best GLS models including climate, DBH, and year for Niobrara (Nebraska, USA)"
GLS_LT_legend = "Figure S32. Best GLS models including climate and DBH for Little Tesuque (New Mexico, USA)"
GLS_LT_year_legend = "Figure S33. Best GLS models including climate, DBH, and year for Little Tesuque (New Mexico, USA)"
GLS_CB_legend = "Figure S34. Best GLS models including climate and DBH for Cedar Breaks (Utah, USA)"
GLS_CB_year_legend = "Figure S35. Best GLS models including climate, DBH, and year for Cedar Breaks (Utah, USA)"
GLS_SC_legend = "Figure S36. Best GLS models including climate and DBH for Scotty Creek (Northwest Territory, Canada)"
GLS_SC_year_legend = "Figure S37. Best GLS models including climate, DBH, and year for Scotty Creek (Northwest Territory, Canada)"

SC_1970break_legend = "Figure S38. Climate responses at Scotty Creek (Northwest Territory, Canada) before and after 1970."

RW_interactions_all_legend = "Figure S39. (RW_interactions_all)"
BAI_interactions_all_legend ="Figure S40. (BAI_interactions_all)"

decadal_plot_BCNM_legend = "Figure S41. (Decadal BCNM)"
decadal_plot_HKK_legend = "Figure S42. (Decadal HKK)"
decadal_plot_SCBI_legend = "Figure S43. (Decadal SCBI)"
decadal_plot_LDW_legend = "Figure S44. (Decadal LDW)"
decadal_plot_HF_legend = "Figure S45. (Decadal HF)"
decadal_plot_ZOF_legend = "Figure S46. (Decadal ZOF)"
decadal_plot_NIO_legend = "Figure S47. (Decadal NIO)"
decadal_plot_LT_legend = "Figure S48. (Decadal LT)"
decadal_plot_CB_legend = "Figure S49. (Decadal CB)"
decadal_plot_SC_legend = "Figure S50. (Decadal SC)"

@@

@@

\newpage
## `r climwin_sameV_sameW_legend`
![](tables_figures/SI_figures/climwin_plots_combined/SCBI_pre.png)

**`r climwin_sameV_sameW_legend`** Here, *climwin* identified **GIVE WINDOW** precipitation ($PPT$) as the strongest climate variable across all four analyses ($RW$ with and without trees for which $DBH$ could not be reconstructed, $BAI$, $\Delta AGB$).

\newpage
## `r climwin_sameV_diffW_legend`
![](tables_figures/SI_figures/climwin_plots_combined/SCBI_pet.png)

**`r climwin_sameV_diffW_legend`** Here, *climwin* identified potential evapotranspiration ($PET$) as the strongest climate variable across all four analyses ($RW$ with and without trees for which $DBH$ could not be reconstructed, $BAI$, $\Delta AGB$), but a different window (**GIVE WINDOW**) was chosen for  $BAI$ and $\Delta AGB$ than for $RW$ (**GIVE WINDOW**).

\newpage
## `r climwin_diffV_diffW_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HKK_tmp_tmx.png)

**`r climwin_diffV_diffW_legend`** Here....

>>>>

all_climwin = "S15-S34"
climwin_BCNM_W = "S15"
climwin_BCNM_T = "S16"
climwin_HKK_W = "S17"
climwin_HKK_T = "S18"
climwin_SCBI_W = "S19"
climwin_SCBI_T = "S20"

all_GLS = "S35-S54"
GLS_BCNM = "S35"
GLS_BCNM_year = "S36"
GLS_HKK = "S37"
GLS_HKK_year = "S38"
GLS_SCBI = "S39"
GLS_SCBI_year = "S40"
GLS_LDW = "S41"
GLS_LDW_year = "S42"
GLS_HF = "S343"
GLS_HF_year = "S44"
GLS_ZOF = "S45"
GLS_ZOF_year = "S46"
GLS_NIO = "S47"
GLS_NIO_year = "S48"
GLS_LT = "S49"
GLS_LT_year = "S50"
GLS_CB = "S51"
GLS_CB_year = "S52"
GLS_SC = "S53"
GLS_SC_year = "S54"

SC_1970break = "S55"

RW_interactions_all= "S56"
BAI_interactions_all= "S57"

decadal_analysis_figs_all = "S58-S67"
decadal_plot_BCNM = "S58"
decadal_plot_HKK = "S59"
decadal_plot_SCBI = "S60"
decadal_plot_LDW = "S61"
decadal_plot_HF = "S62"
decadal_plot_ZOF = "S63"
decadal_plot_NIO = "S64"
decadal_plot_LT = "S65"
decadal_plot_CB = "S66"
decadal_plot_SC = "S67"

@@

climwin_BCNM_W_legend = "Figure S15. Climwin output for water variable group at BCNM."
climwin_BCNM_T_legend = "Figure S16. Climwin output for temperature variable group at BCNM."
climwin_HKK_W_legend =  "Figure S17. Climwin output for water variable group at HKK."
climwin_HKK_T_legend = "Figure S18. Climwin output for temperature variable group at HKK."
climwin_SCBI_W_legend  = "Figure S19. Climwin output for water variable group at SCBI."
climwin_SCBI_T_legend = "Figure S20. Climwin output for temperature variable group at SCBI."
climwin_LDW_W_legend = "Figure S21. Climwin output for water variable group at LDW."
climwin_LDW_T_legend = "Figure S22. Climwin output for temperature variable group at LDW."
climwin_HF_W_legend =  "Figure S23. Climwin output for water variable group at HF."
climwin_HF_T_legend = "Figure S23. Climwin output for temperature variable group at HF."
climwin_ZOF_W_legend  = "Figure S25. Climwin output for water variable group at ZOF."
climwin_ZOF_T_legend = "Figure S26. Climwin output for temperature variable group at ZOF."
climwin_NIO_W_legend = "Figure S27. Climwin output for water variable group at NIO."
climwin_NIO_T_legend = "Figure S28. Climwin output for temperature variable group at NIO."
climwin_LT_W_legend =  "Figure S29. Climwin output for water variable group at LT."
climwin_LT_T_legend = "Figure S30. Climwin output for temperature variable group at LT."
climwin_CB_W_legend  = "Figure S31. Climwin output for water variable group at CB."
climwin_CB_T_legend = "Figure S32. Climwin output for temperature variable group at CB."
climwin_SC_W_legend  = "Figure S33. Climwin output for water variable group at SC."
climwin_SC_T_legend = "Figure S34. Climwin output for temperature variable group at SC."

GLS_BCNM_legend = "Figure S35. Best GLS models including climate and DBH for Barro Colorado Nature Monument (Panama)"
GLS_BCNM_year_legend = "Figure S36. Best GLS models including climate, DBH, and year for Barro Colorado Nature Monument (Panama)"
GLS_HKK_legend = "Figure S37. Best GLS models including climate and DBH for Huai Kha Khaeng (Thailand)"
GLS_HKK_year_legend = "Figure S38. Best GLS models including climate, DBH, and year for Huai Kha Khaeng (Thailand)"
GLS_SCBI_legend = "Figure S39. Best GLS models including climate and DBH for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_SCBI_year_legend = "Figure S40. Best GLS models including climate, DBH, and year for the Smithsonian Conservation Biology Institute (Virginia, USA)"
GLS_LDW_legend = "Figure S41. Best GLS models including climate and DBH for Lilley Dickey Woods (Indiana, USA)"
GLS_LDW_year_legend = "Figure S42. Best GLS models including climate, DBH, and year for Lilley Dickey Woods (Indiana, USA)"
GLS_HF_legend = "Figure S43. Best GLS models including climate and DBH for Harvard Forest (Massachusetts, USA)"
GLS_HF_year_legend = "Figure S44. Best GLS models including climate, DBH, and year for Harvard Forest (Massachusetts, USA) "
GLS_ZOF_legend = "Figure S45. Best GLS models including climate and DBH for Zofin Forest (Czech Republic)"
GLS_ZOF_year_legend = "Figure S46. Best GLS models including climate, DBH, and year for Zofin Forest (Czech Republic)"
GLS_NIO_legend = "Figure S47. Best GLS models including climate and DBH for Niobrara (Nebraska, USA)"
GLS_NIO_year_legend = "Figure S48. Best GLS models including climate, DBH, and year for Niobrara (Nebraska, USA)"
GLS_LT_legend = "Figure S49. Best GLS models including climate and DBH for Little Tesuque (New Mexico, USA)"
GLS_LT_year_legend = "Figure S50. Best GLS models including climate, DBH, and year for Little Tesuque (New Mexico, USA)"
GLS_CB_legend = "Figure S51. Best GLS models including climate and DBH for Cedar Breaks (Utah, USA)"
GLS_CB_year_legend = "Figure S52. Best GLS models including climate, DBH, and year for Cedar Breaks (Utah, USA)"
GLS_SC_legend = "Figure S53. Best GLS models including climate and DBH for Scotty Creek (Northwest Territory, Canada)"
GLS_SC_year_legend = "Figure S54. Best GLS models including climate, DBH, and year for Scotty Creek (Northwest Territory, Canada)"

SC_1970break_legend = "Figure S55. Climate responses at Scotty Creek (Northwest Territory, Canada) before and after 1970."

RW_interactions_all_legend = "Figure S56. (RW_interactions_all)"
BAI_interactions_all_legend ="Figure S57. (BAI_interactions_all)"

decadal_plot_BCNM_legend = "Figure S58. (Decadal BCNM)"
decadal_plot_HKK_legend = "Figure S59. (Decadal HKK)"
decadal_plot_SCBI_legend = "Figure S60. (Decadal SCBI)"
decadal_plot_LDW_legend = "Figure S61. (Decadal LDW)"
decadal_plot_HF_legend = "Figure S62. (Decadal HF)"
decadal_plot_ZOF_legend = "Figure S63. (Decadal ZOF)"
decadal_plot_NIO_legend = "Figure S64. (Decadal NIO)"
decadal_plot_LT_legend = "Figure S65. (Decadal LT)"
decadal_plot_CB_legend = "Figure S66. (Decadal CB)"
decadal_plot_SC_legend = "Figure S67. (Decadal SC)"

@@

climwin_generic = " **(generic legend)**"

@@

\newpage
## `r climwin_BCNM_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/BCI_pre.png)

**`r climwin_BCNM_W_legend`** `r climwin_generic`

\newpage
## `r climwin_BCNM_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/BCI_tmn.png)

**`r climwin_BCNM_T_legend`** `r climwin_generic`

\newpage
## `r climwin_HKK_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HKK_wet.png)

**`r climwin_HKK_W_legend`** `r climwin_generic`

\newpage
## `r climwin_HKK_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HKK_tmp_tmx.png)

**`r climwin_HKK_T_legend`** `r climwin_generic`

\newpage
## `r climwin_SCBI_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/SCBI_pre.png)

**`r climwin_SCBI_W_legend`** `r climwin_generic`

\newpage
## `r climwin_SCBI_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/SCBI_pet.png)

**`r climwin_SCBI_T_legend`** `r climwin_generic`

\newpage
## `r climwin_LDW_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/LillyDickey_pre.png)

**`r climwin_LDW_W_legend`** `r climwin_generic`

\newpage
## `r climwin_LDW_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/LillyDickey_pet.png)

**`r climwin_LDW_T_legend`** `r climwin_generic`

\newpage
## `r climwin_HF_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HarvardForest_pre_wet.png)

**`r climwin_HF_W_legend`** `r climwin_generic`

\newpage
## `r climwin_HF_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/HarvardForest_pet.png)

**`r climwin_HF_T_legend`** `r climwin_generic`

\newpage
## `r climwin_ZOF_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Zofin_wet.png)

**`r climwin_ZOF_W_legend`** `r climwin_generic`

\newpage
## `r climwin_ZOF_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Zofin_tmx.png)

**`r climwin_ZOF_T_legend`** `r climwin_generic`

\newpage
## `r climwin_NIO_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Niobara_pre.png)

**`r climwin_NIO_W_legend`** `r climwin_generic`

\newpage
## `r climwin_NIO_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/Niobara_tmx.png)

**`r climwin_NIO_T_legend`** `r climwin_generic`

\newpage
## `r climwin_LT_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/NewMexico_pre.png)

**`r climwin_LT_W_legend`** `r climwin_generic`

\newpage
## `r climwin_LT_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/NewMexico_tmx.png)

**`r climwin_LT_T_legend`** `r climwin_generic`

\newpage
## `r climwin_CB_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/CedarBreaks_pre.png)

**`r climwin_CB_W_legend`** `r climwin_generic`

\newpage
## `r climwin_CB_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/CedarBreaks_tmx.png)

**`r climwin_CB_T_legend`** `r climwin_generic`

\newpage
## `r climwin_SC_W_legend`
![](tables_figures/SI_figures/climwin_plots_combined/ScottyCreek_pre.png)

**`r climwin_SC_W_legend`** `r climwin_generic`

\newpage
## `r climwin_SC_T_legend`
![](tables_figures/SI_figures/climwin_plots_combined/ScottyCreek_tmx.png)

**`r climwin_SC_T_legend`** `r climwin_generic`
